---
title: "Univariate Categorical Variable"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{univariate-categorical}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Setup

Type `library(statdata)` and then, datasets in the `statdata` package are avaiable.

```{r setup}
library(tidyverse)
library(statdata)
```

# Load Sample Dataset

`gender` dataset contains male and female row-by-row values.


```{r gender}
data("gender")
gender <- gender %>% 
  set_names("gender")

gender
```

# Basic Analysis

The univariate categorical variable can be summarized through counting.

```{r basic-analysis}

gender %>%
  count(gender)
```


# Visualization

We can visualize the univariate categorical variable with barplot or pie chart.

```{r basic-visualization}
par(family = "NanumGothic")

gender_count <- gender %>%
  count(gender)

barplot(n ~ gender, data = gender_count)
```

The pie chart plot is also possible.

```{r basic-visualization-pie}
par(family = "NanumGothic")

gender_vector <- gender_count %>% 
  pull(n)

names(gender_vector) <- gender_count$gender

pie(gender_vector)
```
