---
title: "Univariate Continous Variable"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{univariate-continuous}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Setup

Type `library(statdata)` and then, datasets in the `statdata` package are avaiable.

```{r setup}
library(dplyr)
library(readr)
library(magrittr)
library(purrr)
library(fs)
library(skimr)
library(statdata)


```

# Load Sample Dataset

`kicks_num` dataset contains number of success in the traditional Korean game, `Jegichagi`.


```{r kick-num}
data("kicks_num")
kicks_num <- kicks_num %>% 
  set_names('count')

kicks_num
```

# Basic Analysis

[`skimr`](https://cran.r-project.org/web/packages/skimr/) package contains `skim()` function, which is an improved version of `summary` function. This one line command spits out all the descriptive statstics needed to understand the continuous variable.

```{r basic-analysis}
skimr::skim(kicks_num)
```


# Visualization

We can visualize the univariate continouse variable with histogram or stem-and-leaf plot.
There are various ways to visualize histogram, but the simplest way is to use `hist()`.

```{r basic-visualization}
hist(kicks_num$count)
```

The stem-and-leaf plot is also possible.

```{r basic-visualization-stem}
stem(kicks_num$count)
```
